---
title: "Extortion in Mexico: Who pays and why?"
author: "Patricio R. Estevez Soto"
email: "patricio.estevez.14@ucl.ac.uk"
date: "05/05/2018"
output:
  md_document:
    variant: "markdown"
pandoc_args: "--smart"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment="",
                      cache=TRUE,
                      #dev=c("png", "CairoPDF"),
                      error=TRUE)
options(knitr.kable.NA = '---')
```

# Introduction

This document contains the script and results for a research project on extortion against businesses in Mexico.

Previous research has found that extortion against businesses is acutely concentrated on a few businesses who experience more than half of all extortion incidents in the country as repeat extortion victimizations. That project found that the rate at which businesses suffer extortion is mostly determined by their characteristics---such as their age, whether they are a restaurant, the number of corruption incidents they have suffered, and their size---and to a lesser extent, to the characteristics of the state where they are located---which include the state homicide rate and other unmeasured between-state differences.

Nonetheless, that research did not consider that most extortion victims do not comply with extortion demands. Thus this project aims to explore the distribution of successful extortion incidents, and identify the incident, victim and area characteristics associated with a higher likelihood of complying with extortion.

The incident-level characteristics that will be explored are:

- month
- time of day
- number of offenders
- victim's relationship to the offender
- use of a weapon
- type of weapon
- use of violence
- whether the incident was reported to the authorities (MP + other)
- type of extortion
- what was requested
- retaliation against business for not complying
- whether the victim complied with the extortion

The victim-level characteristics are:
- business type
- business age
- business size
- Victim of corruption
- number of corruption victimizations, repeat corruption victim
- number of extortion victimizations
- repeat extortion victim

Area-level characteristics:
- State
- State homicides
- State population (control)
Add more stuff here

# Set up, data input and pre-process

## Session info

We first check details of the session and system, and for reproducibility, we set the random seed.

```{r session, cache=FALSE}
starttime <- proc.time()
date()
sessionInfo()
set.seed(42)
options(scipen=0)
```

## Load packages and functions

Next we load the packages that we will use.

```{r packages}

#library(Cairo)
#library(glmmTMB)
library(victim)
library(tidyverse)
library(downloader)
library(sandwich)
library(lmtest)

read.dbf <- foreign::read.dbf
getURL <- RCurl::getURL
kable <- knitr::kable
melt <- reshape2::melt
select <- dplyr::select
getURL <- RCurl::getURL


sessionInfo()

```

required packages thus far:

- `foreign`
- `classInt`
- `tidyverse`
- `RCurl`
- `victim`
- `knitr`
- `lmtest`
- `lazyeval`
- `car`
- `devtools`
- `sandwich`
- `downloader`



Load custom functions

```{r functions}

mylog <- function(x, center = FALSE)
{
    if(min(x) <= 0) {tlog <- log1p}
    else {tlog <- log}

    logx <- tlog(x)

    if(isTRUE(center))
    {
        logx <- logx - tlog(mean(x))
    }

    return(logx)

}

multi_glm <- function(data, response, predictor, family = binomial(), ...)
{
    # Function that fits a glm and returns:
    # slope, slope p value, loglik, LR Test p value,

    glm_form <- y ~ x
    lazyeval::f_lhs(glm_form) <- lazyeval::uq(response)
    lazyeval::f_rhs(glm_form) <- lazyeval::uq(predictor)

    mod <- glm(formula = glm_form, data = data, family = family, ...)

    # Gather results into a data frame
    out = data.frame(slope = coef(mod)[2:length(coef(mod))],
                     pval = summary(mod)$coefficients[2:length(coef(mod)),4])

    out$s1 <- victim::add_stars(out$pval)

    out2 <- data.frame(ll = logLik(mod)[1],
                      LRTpval = anova(mod, test = "LRT")[2,5])
    out2$s2 <- victim::add_stars(out2$LRTpval)

    out[1,4] <- out2$ll
    out[1,5] <- out2$LRTpval
    out[1,6] <- out2$s2
    names(out)[4:6] <- names(out2)
    # out <- cbind(out,out2)

    return(out)
}

vif <- function(form, data, family = "binomial")
{
    if(!is_formula(form)) {form <- formula(form)}

    lmmod <- glm(form, data = data,  family = family)

    vifs <- car::vif(lmmod)

    return(vifs)
}

null_glm_ll <- function(dv, data, family = binomial(), ...)
{
    glm_form <- y ~ 1
    lazyeval::f_lhs(glm_form) <- lazyeval::uq(dv)

    model <-  glm(formula = glm_form, data = data, family = family, ...)

    out <- data.frame(slope = NA,
                      pval = NA,
                      s1 = NA,
                      ll= logLik(model),
                      LRTpval = NA,
                      s2 = NA)
    rownames(out) <- "Null"
    return(out)
}


propfun <- function(dv, w, iv, dat)
{
    dat %>%
        group_by_(iv) %>%
        summarise_(lazyeval::interp(~ sum(x), x = as.name(dv)),
                   lazyeval::interp(~ sum(x), x = as.name(w))) -> dat2

    dat2 <- data.frame(dat2)

    pt <- prop.test(dat2[,2], dat2[,3])

    names(pt$estimate) <- dat2[,iv]
    pt$data.name <- paste0(dv, " out of ", w)
    return(pt)
}

tmbresults <- function(tmbmodel)
{
    print(summary(tmbmodel))
    print("Confidence Intervals (Log-odds)")
    print(confint(tmbmodel))
    # print("Confidence Intervals (Odd Ratio)")
    # print(exp(confint(tmbmodel)))
    print(lmtest::waldtest(tmbmodel, test = "Chisq"))
    #print("Variance-Covariance Matrix")
    #print(vcov(tmbmodel))

}

dropalltest <- function(mod)
{
    dropped <- drop1(mod, test = "Chisq", trace = TRUE)
    print(dropped)
    print(kable(cbind(dropped, sig = add_stars(dropped$`Pr(>Chi)`))))
}


deff_cl <- function(mod, rob_mod) diag(mod$var)/diag(rob_mod$var)


summaryCL <- function(m, clusterid, conf.level = 0.95, boots = FALSE, R = 400, ...)
{
    if(isFALSE(boots))
    {
        robust_vcov <- sandwich::vcovCL(m, cluster = clusterid)
    } else
    {
        robust_vcov <- sandwich::vcovBS(m, cluster = clusterid, R, ...)
    }
    
    
    rob_coef <- lmtest::coeftest(m, vcov. = robust_vcov)
    rob_confint <- lmtest::coefci(m, level = conf.level, vcov. = robust_vcov)
    
    results <- cbind(rob_coef, rob_confint)
    results <- data.frame(results)
    
    names(results) <- c("estimate", "SE", "z.value", "p.value", "ci.low", "ci.high")
    
    results$sig <- victim::add_stars(results[,4])
    
    waldt <- lmtest::waldtest(m, vcov = robust_vcov, test = "Chisq")
    
    results_list <- list(coefs = results, clusterid = clusterid, wald = waldt, vcov = robust_vcov)
    
    class(results_list) <- "summaryCL"
    
    return(results_list)
    
}


print.summaryCL <- function(summaryCL.object) 
{
    print(summaryCL.object[-4])
}

vcov.summaryCL <- function(summaryCL.object)
{
    summaryCL.object$vcov
}


```

## Load data

We first load and arrange the area and victim level data

```{r test-setting}

### Change if not in testing settings
testing <- TRUE

if(testing == TRUE)
{
    download("https://raw.githubusercontent.com/prestevez/datahouse/master/enve2014cuest_ciega_2014.dbf",
                  destfile = "enve2014cuest_ciega_2014.dbf", mode = "wb")
    download("https://raw.githubusercontent.com/prestevez/datahouse/master/enve2014delitos_ciega_2014.dbf",
             destfile = "enve2014delitos_ciega_2014.dbf", mode = "wb")

}

list.files()

```


```{r victim-level}
enve_all <- read.dbf("enve2014cuest_ciega_2014.dbf")

cat_entidades <- read.csv(text = getURL("https://raw.githubusercontent.com/prestevez/datahouse/master/cat_entidades.csv"), head=TRUE)
state_level_data <- read.csv(text = getURL("https://raw.githubusercontent.com/prestevez/datahouse/master/state_level_data_2013.csv"), header=TRUE)
state_level_data <- merge(state_level_data,
                          cat_entidades, by="CVE_ENT", all.x=TRUE)
scode <- read.csv(text = getURL("https://raw.githubusercontent.com/prestevez/datahouse/master/secode.csv"), head=TRUE)
scode$Code <- scode$Code*10000

# Prepare data for analysis
# Selecting only the relevant variables

enve_test <- data.frame(extortions=as.integer(as.character(enve_all$P26_10)))

enve_test$extortion_victim <- enve_all$P25_10
enve_test$extortions[enve_test$extortion_victim == 2] <- 0
summary(enve_test$extortions)
table(enve_test$extortions)

enve_test$extortions[is.na(enve_test$extortions)] <- 0

summary(enve_test$extortions)
table(enve_test$extortions)

enve_test$rep_extortion_victim <- factor(enve_test$extortions)
levels(enve_test$rep_extortion_victim) <- c(0, 0,
                    rep(1, length(levels(enve_test$rep_extortion_victim)) - 2))

summary(enve_test$rep_extortion_victim)

enve_test$rep_extortions <- enve_test$extortions
enve_test$rep_extortions[enve_test$rep_extortions > 0] <- enve_test$rep_extortions[enve_test$rep_extortions > 0] - 1

summary(enve_test$rep_extortions)
table(enve_test$rep_extortions)


enve_test$CVE_UNICA <- as.integer(as.character(enve_all$ID_CONSECU))

enve_test$bribes <- as.integer(as.character(enve_all$P33))
summary(enve_test$bribes)

# 4 bribe cats
enve_test$bribe1 <- enve_all$P29_1
enve_test$bribe2 <- enve_all$P30_1
enve_test$bribe3 <- enve_all$P31_1
enve_test$bribe4 <- enve_all$P32_1

enve_test$bribes[with(enve_test,
                        bribe1 == 2 &
                        bribe2 == 2 &
                        bribe3 == 2 &
                        bribe4 == 2)] <- 0

summary(enve_test$bribes)

enve_test$bribes[is.na(enve_test$bribes)] <- 0

enve_test$bribe_victim <- factor(enve_test$bribes)
levels(enve_test$bribe_victim) <- c(0,
                                    rep(1, length(levels(enve_test$bribe_victim)) - 1))
summary(enve_test$bribe_victim)

enve_test$rep_bribe <- factor(enve_test$bribes)
levels(enve_test$rep_bribe) <- c(0, 0, rep(1,
                                           length(levels(enve_test$rep_bribe)) - 2))
summary(enve_test$rep_bribe)

enve_test$bribe_cats <- factor(enve_test$bribes)
levels(enve_test$bribe_cats) <- c(0, 1, 2, rep("3+",
                                            length(levels(enve_test$bribe_cats)) - 3))
summary(enve_test$bribe_cats)

enve_test$CVE_ENT <- as.integer(as.character(enve_all$CVE_ENT))

enve_test$size <- enve_all$ID_ESTRATO
levels(enve_test$size) <- c("Large", "Medium", "Small", "Micro")

enve_test$sector <- enve_all$SECTOR_FIN

# subsector
enve_test$tempsub <- as.integer(as.character(enve_all$P1_1B))
enve_test$subsector <- cut(enve_test$tempsub, scode$Code, right=FALSE)
levels(enve_test$subsector) <- scode$Sector
enve_test$subsector <- droplevels(enve_test$subsector)
enve_test$subsector <- relevel(enve_test$subsector, ref="Retail")
levels(enve_test$subsector)

enve_test$subsector_safe <- enve_test$subsector

enve_test$subsector <- as.character(enve_test$subsector)

enve_test$subsector[enve_test$subsector %in%
                      c("Mining",
                        "Utilities",
                        "Construction")] <- "Industry"

enve_test$subsector[enve_test$subsector %in%
                      c("Media",
                        "Maintenance",
                        "Other",
                        "Corporate",
                        "Finance",
                        "Health",
                        "Leisure",
                        "Education",
                        "Prof. services",
                        "Real estate")] <- "Other serv."


enve_test$subsector <- as.factor(enve_test$subsector)
enve_test$subsector <- relevel(enve_test$subsector, ref="Retail")
levels(enve_test$subsector)
summary(enve_test$subsector)

enve_test$years <- 2013 - as.numeric(as.character(enve_all$P3))
summary(enve_test$years)

intyears <- classInt::classIntervals(enve_test$years, 5, style="quantile")
enve_test$yearsquant <- cut(enve_test$years, intyears$brks, right=TRUE,
                            include.lowest = TRUE)

enve_test <- merge(enve_test, state_level_data, by="CVE_ENT", all.x=TRUE)

length(enve_test$extortions[is.na(enve_test$extortions)])
length(enve_test$bribes[is.na(enve_test$bribes)])

## enve_test$extortions[is.na(enve_test$extortions)] <- 0
## enve_test$bribes[is.na(enve_test$bribes)] <- 0

summary(enve_test)

```

Next we load incident-level data:

```{r incident-level}

enve_incidents_all <- read.dbf("enve2014delitos_ciega_2014.dbf")

# Selecting only those relevant for extortion (code 10)

enve_incidents_all$delito <- as.integer(as.character(enve_incidents_all$ID_DELITO))

enve_incidents <- enve_incidents_all[enve_incidents_all$delito == 10,]

# Selecting those relevant for our study

incident_df <- data.frame(CVE_UNICA=as.integer(as.character(enve_incidents$ID_CONSECU)))

incident_df$delito <- enve_incidents$delito

incident_df$n_offenders <- enve_incidents$M1_8
summary(incident_df$n_offenders)
levels(incident_df$n_offenders) <- c(1:3, "4+", "4+", "4+", "DK/DA")
summary(incident_df$n_offenders)

incident_df$n_offenders_NA <-  incident_df$n_offenders
incident_df$n_offenders_NA[is.na(incident_df$n_offenders)] <- "DK/DA"
summary(incident_df$n_offenders_NA)

incident_df$uk_n_offenders <- incident_df$n_offenders_NA
levels(incident_df$uk_n_offenders)[1:4] <- "known"

incident_df$n_offenders_num <- enve_incidents$M1_8
summary(incident_df$n_offenders_num)
levels(incident_df$n_offenders_num) <- c(1:6, 0)
summary(incident_df$n_offenders_num)
incident_df$n_offenders_num[is.na(incident_df$n_offenders_num)] <- 0
incident_df$n_offenders_num <- as.numeric(as.character(incident_df$n_offenders_num))
table(incident_df$n_offenders_num)

incident_df$n_offenders_num <- incident_df$n_offenders_num - 1


## Data imputation for missing variables?

incident_df$rel_offenders <- enve_incidents$M1_11
levels(incident_df$rel_offenders) <- c("Known", "Known",
                                       "Known", "Known",
                                       "Total stranger", "DK/DA")
incident_df$rel_offenders <- relevel(incident_df$rel_offenders, ref="Total stranger")
summary(incident_df$rel_offenders)

incident_df$rel_offenders_NA <- incident_df$rel_offenders
incident_df$rel_offenders_NA[is.na(incident_df$rel_offenders_NA)] <- "DK/DA"
summary(incident_df$rel_offenders_NA)

incident_df$had_weapon <- enve_incidents$M1_13
levels(incident_df$had_weapon) <- c("Yes", "No", "DK/DA")
incident_df$had_weapon <- relevel(incident_df$had_weapon, ref="No")
summary(incident_df$had_weapon)

incident_df$had_weapon_NA <- incident_df$had_weapon
incident_df$had_weapon_NA[is.na(incident_df$had_weapon_NA)] <- "DK/DA"
summary(incident_df$had_weapon_NA)

incident_df$extortion_type <- as.character(enve_incidents$M5_1)
incident_df$extortion_type <- as.factor(incident_df$extortion_type)
levels(incident_df$extortion_type) <- c("Remote", "Remote", "Street",
                                        "Premises", "Cobro de piso", "Other")
levels(incident_df$extortion_type)
summary(incident_df$extortion_type)

incident_df$extortion_type_bin <- as.character(enve_incidents$M5_1)
incident_df$extortion_type_bin <- as.factor(incident_df$extortion_type_bin)
levels(incident_df$extortion_type_bin) <- c("Remote", "Remote", "In person",
                                        "In person", "In person", "Other")
levels(incident_df$extortion_type_bin)
summary(incident_df$extortion_type_bin)

incident_df$complied <- enve_incidents$M5_3
levels(incident_df$complied) <-  c("Yes", "No", "DK/DA")
incident_df$complied <- relevel(incident_df$complied, ref="No")
summary(incident_df$complied)


incident_df$complied_bin <- enve_incidents$M5_3
levels(incident_df$complied_bin) <-  c("Yes", "No", NA)
incident_df$complied_bin <- relevel(incident_df$complied_bin, ref="No")
summary(incident_df$complied_bin)

incident_df$complied_bin_NA <- incident_df$complied_bin
incident_df$complied_bin_NA[is.na(incident_df$complied_bin_NA)] <- "No"
summary(incident_df$complied_bin_NA)

incident_df <- subset(incident_df, extortion_type != "Other")
incident_df$extortion_type <- droplevels(incident_df$extortion_type)
incident_df$extortion_type_bin <- droplevels(incident_df$extortion_type_bin)

summary(incident_df)
```

Next we merge both incident-level and victim-level tables.

```{r incident-victim-merge}
enve_incvic <- merge(incident_df, enve_test, by="CVE_UNICA")

nrow(enve_incvic)
nrow(incident_df)
```


# EDA

Very simple tests.

First. Mann-Whitney test of number of offenders and compliance, per ext type.

```{r mann-whitney}

wilcox.test(n_offenders_num ~ complied_bin_NA, data = enve_incvic,
            subset = n_offenders_num > -1)

wilcox.test(n_offenders_num ~ complied_bin, data = enve_incvic,
            subset = n_offenders_num > -1)

### according to extortion type

t.test(n_offenders_num ~ complied_bin_NA, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "In person")

wilcox.test(n_offenders_num ~ complied_bin_NA, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "In person")

t.test(n_offenders_num ~ complied_bin_NA, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "Remote")

wilcox.test(n_offenders_num ~ complied_bin_NA, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "Remote")


# Repeat for excluding na

t.test(n_offenders_num ~ complied_bin, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "In person")

wilcox.test(n_offenders_num ~ complied_bin, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "In person")

t.test(n_offenders_num ~ complied_bin, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "Remote")

wilcox.test(n_offenders_num ~ complied_bin, data = enve_incvic,
            subset = n_offenders_num > -1 & extortion_type_bin == "Remote")

```

Second. Relationship to offender by ext type.


```{r relationship-ext-type}
comp_rel <- batch_chisq(enve_incvic, "complied_bin_NA", "rel_offenders_NA")
comp_rel

print_kables(chisq_list(comp_rel, print_option = "pandoc", option = "observed"))
print_kables(chisq_list(comp_rel, print_option = "pandoc", option = "ratio"))

# Subset for in person extortions

comp_rel_ip <- batch_chisq(subset(enve_incvic, extortion_type_bin == "In person"), 
                           "complied_bin_NA", "rel_offenders_NA")
comp_rel_ip

print_kables(chisq_list(comp_rel_ip, print_option = "pandoc", option = "observed"))
print_kables(chisq_list(comp_rel_ip, print_option = "pandoc", option = "ratio"))

## subset for remote

comp_rel_rmt <- batch_chisq(subset(enve_incvic, extortion_type_bin == "Remote"), 
                           "complied_bin_NA", "rel_offenders_NA")
comp_rel_rmt

print_kables(chisq_list(comp_rel_rmt, print_option = "pandoc", option = "observed"))
print_kables(chisq_list(comp_rel_rmt, print_option = "pandoc", option = "ratio"))

```

Third. Redo situational aggravants (weapons et al) using in person subset only.


```{r aggravants}

comp_wpn <- batch_chisq(enve_incvic, "complied_bin_NA", "had_weapon_NA")
comp_wpn

print_kables(chisq_list(comp_wpn, print_option = "pandoc", option = "observed"))
print_kables(chisq_list(comp_wpn, print_option = "pandoc", option = "ratio"))

# Subset for in person extortions

comp_wpn_ip <- batch_chisq(subset(enve_incvic, extortion_type_bin == "In person"), 
                           "complied_bin_NA", "had_weapon_NA")
comp_wpn_ip

print_kables(chisq_list(comp_wpn_ip, print_option = "pandoc", option = "observed"))
print_kables(chisq_list(comp_wpn_ip, print_option = "pandoc", option = "ratio"))

## subset for remote

comp_wpn_rmt <- batch_chisq(subset(enve_incvic, extortion_type_bin == "Remote"), 
                           "complied_bin_NA", "had_weapon_NA")
comp_wpn_rmt

print_kables(chisq_list(comp_wpn_rmt, print_option = "pandoc", option = "observed"))
print_kables(chisq_list(comp_wpn_rmt, print_option = "pandoc", option = "ratio"))

```

# Models


```{r subset-no-NA}

## datasets with no NA values first.

nacols <- colnames(enve_incvic)[colSums(is.na(enve_incvic)) > 0]

nonacols <- names(enve_incvic)[!(names(enve_incvic) %in% nacols)]

enve_incvic %>%
    select(nonacols) -> enve_nona

summary(enve_nona)
nrow(enve_nona)
nrow(enve_nona[complete.cases(enve_nona),])
nrow(enve_nona[complete.cases(enve_incvic),])

## Data structure

"number of incidents"
nrow(enve_nona)

"incidents per business"
table(table(enve_nona$CVE_UNICA))
enve_nona %>%
    count(CVE_UNICA) %>%
    summarise(min(n),
              max(n),
              mean(n),
              n())

"number of incidents per state"
enve_nona %>%
    count(CVE_ENT) %>%
    summarise(min(n),
              mean(n),
              max(n),
              n())

"number of businesses per state"
enve_nona %>%
    count(CVE_ENT, CVE_UNICA) %>%
    count(CVE_ENT) %>%
    summarise(min(nn),
              mean(nn),
              max(nn))

```


First the canonical model with the state level variables identified in JQC manuscript.

A polynomial for the years variable creates too large estimates. Better to use yearsquant or log years.



```{r models-1}


compliance_formula <- complied_bin_NA ~ extortion_type +
                                        n_offenders_NA +
                                        had_weapon_NA +
                                        mylog(extortions) +
                                        mylog(bribes) +
                                        subsector +
                                        size +
                                        yearsquant +
                                        mylog(bribes_abvic, TRUE) +
                                        mylog(armas, TRUE) +
                                        mylog(drogas, TRUE) +
                                        mylog(poblacion, TRUE) +
                                        mylog(N, TRUE) +
                                        scale(General, scale = FALSE) +
                                        scale(Derecho, scale = FALSE)

m1 <- glm(formula = compliance_formula, data = enve_nona, family = binomial())  

tmbresults(m1)
vif(m1, data = enve_nona) 

msum <- summary(m1)

dropalltest(m1)

m1_step <- step(m1, direction = "both")

tmbresults(m1_step)

waldtest(m1_step, m1, test = "Chisq")

```

```{r models-2-by-level}

### Formula for levels

compliance_formula_inc <- complied_bin_NA ~ extortion_type +
                                        n_offenders_NA +
                                        had_weapon_NA

## business only

compliance_formula_bus <- complied_bin_NA ~ mylog(extortions) +
                                        mylog(bribes) +
                                        subsector +
                                        size +
                                        yearsquant


## state only

compliance_formula_state <- complied_bin_NA ~ mylog(bribes_abvic, TRUE) +
                                        mylog(armas, TRUE) +
                                        mylog(drogas, TRUE) +
                                        mylog(poblacion, TRUE) +
                                        mylog(N, TRUE) +
                                        scale(General, scale = FALSE) +
                                        scale(Derecho, scale = FALSE)

## progressive add of levels

compliance_formula_inc_bus <- complied_bin_NA ~ extortion_type +
                                        n_offenders_NA +
                                        had_weapon_NA +
                                        mylog(extortions) +
                                        mylog(bribes) +
                                        subsector +
                                        size +
                                        yearsquant

## incident level vars only

m1_inc <- update(m1, compliance_formula_inc)
tmbresults(m1_inc)

dropalltest(m1_inc)

waldtest(m1_inc, m1, test = "Chisq")

# bus level vars only

m1_bus <- update(m1, compliance_formula_bus)
tmbresults(m1_bus)

dropalltest(m1_bus)

# state level vars only

m1_state <- update(m1, compliance_formula_state)
tmbresults(m1_state)

dropalltest(m1_state)

#### progressive

m1_inc_bus <- update(m1, compliance_formula_inc_bus)
tmbresults(m1_inc_bus)
dropalltest(m1_inc_bus)

### Tests significance of state
waldtest(m1_inc_bus, m1, test = "Chisq")

### Tests significance of busness (in absence of state)

waldtest(m1_inc, m1_inc_bus, test = "Chisq")

# Tests business and state levels
waldtest(m1_inc, m1_inc_bus, m1, test = "Chisq")

mnull <- update(m1, . ~ 1)

# Tests all levels
waldtest(mnull, m1_inc, m1_inc_bus, m1, test = "Chisq")

```

# Use Robust Clustered Errors

Come up with a systematic approach to calculate robust clustered SEs using vcovCL and vcovBS.

Cluster by business and state.


```{r clustered-SE-asym}

# m1, m1step, m1_inc,  m1_bus, m1_state, m1_inc_bus

#### Asymptotic Cluster SE
## Individual-level clustering

cluster_form <- ~ CVE_UNICA + CVE_ENT

m1CL <- summaryCL(m1, cluster_form)
m1CL

m1_stepCL <- summaryCL(m1_step, cluster_form)
m1_stepCL

waldtest(m1_step, m1, test = "Chisq", vcov = vcov(m1CL))

# by levels

## incident level vars only

m1_incCL <- summaryCL(m1_inc, cluster_form)

m1_incCL

waldtest(m1_inc, m1, test = "Chisq", vcov = vcov(m1CL))

# bus level vars only

m1_busCL <- summaryCL(m1_bus, cluster_form)
m1_busCL

# state level vars only

m1_stateCL <- summaryCL(m1_state, cluster_form)
m1_stateCL

#### progressive

m1_inc_busCL <- summaryCL(m1_inc_bus, cluster_form)
m1_inc_busCL


### Tests significance of state
waldtest(m1_inc_bus, m1, test = "Chisq", vcov = vcov(m1CL))

### Tests significance of busness (in absence of state)

waldtest(m1_inc, m1_inc_bus, test = "Chisq", vcov = vcov(m1_inc_busCL))

# Tests business and state levels
waldtest(m1_inc_bus, m1, test = "Chisq", vcov = vcov(m1CL))


### Now repeat for vcovBS 

# m1, m1step, m1_inc,  m1_bus, m1_state, m1_inc_bus

#### Bootstrapped Cluster SE - from sandwich package
## Individual-level clustering

m1BS <- summaryCL(m1, cluster_form, boots = TRUE)
m1BS

m1_stepBS <- summaryCL(m1_step, cluster_form, boots = TRUE)
m1_stepBS

waldtest(m1_step, m1, test = "Chisq", vcov = vcov(m1BS)) 


# by levels

## incident level vars only

m1_incBS <- summaryCL(m1_inc, cluster_form, boots = TRUE)
m1_incBS

waldtest(m1_inc, m1, test = "Chisq", vcov = vcov(m1BS))

# bus level vars only

m1_busBS <- summaryCL(m1_bus, cluster_form, boots = TRUE)
m1_busBS

# state level vars only

m1_stateBS <- summaryCL(m1_state, cluster_form, boots = TRUE)
m1_stateBS

#### progressive

m1_inc_busBS <- summaryCL(m1_inc_bus, cluster_form, boots = TRUE)
m1_inc_busBS


### Tests significance of state
waldtest(m1_inc_bus, m1, test = "Chisq", vcov = vcov(m1BS))

### Tests significance of busness (in absence of state)

waldtest(m1_inc, m1_inc_bus, test = "Chisq", vcov = vcov(m1_inc_busBS))

# Tests business and state levels
waldtest(m1_inc_bus, m1, test = "Chisq", vcov = vcov(m1BS))




```



# Save all to an Rdata file for future analyses

```{r save-all}

nowtime <- Sys.time()
print(nowtime)

filename <- paste0("Estevez_ENVE_Compliance_", nowtime, ".RData")
filename
save.image(file = filename)

```


# Benchmark stats

```{r timing, cache=FALSE}
endtime <- proc.time()
time <- endtime - starttime
time

print(paste("the script took", round(time[3]/60,2),
              "minutes to run.", sep=" "))
```
